Towards a miniKanren with fair search strategies

### 2019-05-24 Paper/paper.tex
BFS

\usepackage{listings}
\lstset{
  language=Scheme,
  basicstyle=\ttfamily,
  morekeywords={run,conde,run*,defrel,==,fresh,disj,conj,disj+},
  alsodigit={!\$\%&*+-./:<=>?@^_~},
  morecomment=[l]{;,\#{}lang},
  mathescape=true,
  literate={-inf}{{$^\infty$}}{1} {/fair}{{$_{fair}$}}{3}
  		   {→}{{$\rightarrow$}}{1}
  		   {×}{{$\times$}}{1}
  		   {==}{{$\equiv$}}{1}
  		   {conde}{{\textcolor[rgb]{0,.3,.7}{\textbf{cond$^e$}}}}{4}
           {appendo}{{append$^o$}}{6}
  		   {repeato}{{repeat$^o$}}{6}
  		   {disj2}{{disj$_2$}}{4}
  		   {conj2}{{conj$_2$}}{4}
  		   {g0}{{g$_0$}}{2}
  		   {g1}{{g$_1$}}{2}
  		   {g2}{{g$_2$}}{2}
  		   {gl}{{g$_l$}}{2}
  		   {gr}{{g$_r$}}{2}
  		   {DFSi }{{DFS$_{i}$}}{3}
  		   {DFSbi}{{DFS$_{bi}$}}{3}
  		   {DFSf }{{DFS$_{f}$}}{3}
}
%% scheme-list .

@@

\newcommand{\DFSi }[0]{DFS$_{i}$}
\newcommand{\DFSf }[0]{DFS$_{f}$}
\newcommand{\DFSbi}[0]{DFS$_{bi}$}
\newcommand{\BFS}[0]{BFS}
\newcommand{\BFSser}[0]{BFS}
\newcommand{\BFSimp}[0]{Our BFS}

@@

We describe fairness levels in disjunction and conjunction
implementations.  Specifically, a disjunction implementation can be
fair, almost-fair, or unfair. And a conjunction implementation can
be fair or unfair.  We compare the fairness level of four search
strategies: the standard miniKanren interleaving depth-first search,
the balanced interleaving depth-first search, the fair depth-first
search, and the standard breadth-first search.
The two non-standard depth-first searches are new. And we present a new, more 
efficient and simpler implementation of the standard breadth-first search. Using 
quantitative evaluation, we argue that the two new depth-first searches are 
competitive alternatives to the standard one, 
and that our breadth-first search implementation is more efficient than 
the current one.

@@

\NOTE[DPF]{I have decided to agree with you that we should not use 
BFSser, so I am going to remove all occurrences.  
Also, we should say, ``Our implementation of BFS''
and then say, shortened to ``Our BFS'' and then you can use it in the table,
so one column should be Our BFS and the other should be BFS.}
\NOTE[DPF]{Occurrences of BFS (without Our) mean Seres et al. (We need only say
that once, or very occasionally}
\NOTE[DPF]{Is the spelling of reverso truly written without the last e?
Shouldn't it be reverseo with the appropriate raising of o.}
\NOTE[LKC]{Yes, it is reverso (not reverseo) in Dmitris' paper}

@@

To summarize our contributions, we
\begin{itemize}
	\item propose and implement \textbf{b}alanced \textbf{i}nterleaving 
depth-first search (\DFSbi{}), a new search strategy with almost-fair \disj{}.
	\item propose and implement \textbf{f}air depth-first search (\DFSf{}), 
a new search strategy with fair \disj{}.
	\item implement in a new way the standard breath-first search (\BFS), a 
search strategy with fair \disj{} and fair \conj{}. We name the current 
implementation by \citeauthor{seres1999algebra} and refer to ``our 
BFS implementation as the improved one. We formally prove
that the two BFS implementations are semantically 
equivalent, however, our BFS implementation runs faster in all 
benchmarks and is shorter.
\end{itemize}

@@

\NOTE[DPF]{Was this supposed to be a note?
``We never use \texttt{run*} in this paper because fairness is only 
 interesting when we have an unbounded number of answers. However, it is 
 perfectly fine to use run* with any search strategies.''}

@@

\BFS{} has both fair \disj{} and fair \conj{}. An easy implementation is based 
on \DFSf{} (not \DFSi{}): (1) replace \texttt{append$^\infty$} with 
\texttt{append$^\infty_{fair}$} in \texttt{append-map$^\infty$}'s body (2) 
rename \texttt{append-map$^\infty$} to \texttt{append-map$^\infty_{fair}$}.

% Our implementation is based 
% on \DFSf{} (not \DFSi{}). To implement \BFS{} based on \DFSf{}, 
% we need \texttt{append-map$^\infty_{fair}$} in addition to 
% \texttt{append$^\infty_{fair}$}. 
% The only difference between \texttt{append-map$^\infty$} and 
% \texttt{append-map$^\infty_{fair}$} is that the latter calls 
% \texttt{append$^\infty_{fair}$} instead of \texttt{append$^\infty$}.

\NOTE[DPF]{I need clarification: Applying the above changes won't result in ``our \BFS,'' but yet a third implementation of \BFS?}

% This implementation is improvable in two ways. First, as mentioned in 
% \autoref{sec:fairconj}, \BFS{} puts answers in bags and answers of the same 
% cost are in the same bag. In this implementation, however, it is unclear where 
% this information is recorded. Second, \texttt{append$^\infty_{fair}$} is 
% extravagant in memory usage. It makes $O(n+m)$ new \texttt{cons} cells every 
% time, where $n$ and $m$ are the ``length''s of input search spaces.

This implementation is improvable in two ways. 
First, as mentioned in \autoref{sec:fairconj}, \BFS{} puts answers in bags and 
answers of the same cost are in the same bag. In our implementation, however, 
we manage cost information subtly---the \texttt{car}s of a search space have 
cost 0 (i.e., they are all in the same bag), and every thunk indicates an 
increment in cost. It is even more subtle that \texttt{append$^\infty_{fair}$} 
and the \texttt{append-map$^\infty_{fair}$} respects the cost information. 
Second, \texttt{append$^\infty_{fair}$} is extravagant in memory usage. It 
makes $O(n+m)$ new \texttt{cons} cells every time, where $n$ and $m$ are the 
``length''s of input spaces.

\NOTE[LKC]{Should I point out that \DFSf{} also has the miserable space 
extravagance?}
\NOTE[DPF]{probably}

In the following subsections, we first describe our improved \BFS{}
implementation that manages cost information in a more clear and concise
way and is less extravagant in memory usage. 
Then we compare our BFS{} with \BFS{}, the 
current implementation by \citeauthor{seres1999algebra}.

\NOTE[DPF]{Let's use one more line and far less horizontal space
by use 3 linefeeds.  They will still align nicely.}

@@

\begin{figure}
	\lstinputlisting{Figures/BFSimp.rkt}	
	\caption{New and changed functions in optimized BFS that implements pure 
	features}
	\label{BFSimp}
\end{figure}

@@

\NOTE[LKC]{I do notice that in the below paragraph the leading sentence is not 
at the beginning (but at the second position). Putting the current first 
sentence at the beginning, however, looks more fun to me.}

@@

\begin{figure}
	\lstinputlisting{Figures/BFSimp-cont.rkt}	
	\caption{New and changed functions in improved BFS that implement impure 
		features}
	\label{BFSimp-cont}
\end{figure}

@@

In this subsection, we compare the pure subset of our BFS with \BFS{}. We 
focus on the pure subset because \BFS{} is designed for a pure 
relational programming system. We prove in Coq that these two search strategies 
are are semantically equivalent, since \texttt{(run n ? g)} produces the same 
result in both our improved \BFS{} and BFS. (See supplements for the formal proof.) To compare efficiency, we 
translate \BFS{}'s Haskell code into Racket (See supplements for the 
translated code). The translation is direct due to the similarity of the two 
relational programming systems. The translated code is longer than our \BFS{}. 
And it runs slower in all benchmarks. Details about differences in efficiency 
are in \autoref{sec:quan}.
% \autoref{compare-efficiency}

@@

\begin{table}
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline 
		benchmark & size & \DFSi{} & \DFSbi{} & \DFSf{} & 
		\BFSimp{} & \BFSser{}  
		\\
		\hline
		\veryrecursiveo & 100000 &  579 &  793 & 2131 & 1438 & 3617 \\
		& 200000 & 1283 & 1610 & 3602 & 2803 & 4212 \\
		& 300000 & 2160 & 2836 &    - & 6137 &    - \\
		\hline 
		\appendo  & 100 &  31 &  41 &  42 &  31 &  68 \\ 
		& 200 & 224 & 222 & 221 & 226 & 218 \\ 
		& 300 & 617 & 634 & 593 & 631 & 622 \\ 
		\hline 
		\reverso & 10 &   5 &   3 &   3 &     38 &     85 \\ 
		& 20 & 107 &  98 &  51 &   4862 &   5844 \\
		& 30 & 446 & 442 & 485 & 123288 & 132159 \\ 
		\hline
		quine-1 & 1 &  71 &  44 & 69 & - & - \\ 
		& 2 & 127 & 142 & 95 & - & - \\ 
		& 3 & 114 & 114 & 93 & - & - \\ 
		\hline
		quine-2 & 1 & 147 & 112 &  56 & - & - \\ 
		& 2 & 161 & 123 & 101 & - & - \\ 
		& 3 & 289 & 189 & 104 & - & - \\ 
		\hline 
		'(I love you)-1 &  99 & 56 & 15 & 22 &  74 & 165 \\ 
		& 198 & 53 & 72 & 55 &  47 &  74 \\
		& 297 & 72 & 90 & 44 & 181 & 365 \\ 
		\hline
		'(I love you)-2 &  99 & 242 &  61 & 16 &  66 &  99 \\ 
		& 198 & 445 & 110 & 60 &  42 &  64 \\
		& 297 & 476 & 146 & 49 & 186 & 322 \\ 
		\hline 
	\end{tabular}
	\caption{The results of a quantitative evaluation: running times of 
	benchmarks 
		in milliseconds}
	\label{compare-efficiency}
\end{table}

In this section, we compare the efficiency of search strategies. A concise 
description is in Table~\ref{compare-efficiency}. A hyphen means ``running out
of memory.'' The first two benchmarks are from 
TRS2. \reverso{} is from 
\citet{rozplokhas2018improving}. The next two benchmarks 
about quine are modified from a similar test case in \citet{byrd2017unified}. 
The modifications are made 
to circumvent the need for symbolic constraints (e.g. $\neq$, 
\texttt{absent$^o$}). Our version generates de 
Bruijnized expressions and prevents closures from being inside a list. The two 
benchmarks differ in the \conde{} clause order of their relational 
interpreters. 
The last two 
benchmarks are about synthesizing expressions that evaluate to \texttt{'(I love 
you)}. This benchmark is from \citet{byrd2017unified}. Again, the 
sibling benchmarks differ in the \conde{} clause order of their relational 
interpreters. The first one 
has elimination rules (i.e. application, \texttt{car}, and \texttt{cdr}) at the 
end, while the other has them at the beginning. We conjecture that \DFSi{} 
would 
perform badly in the second case because elimination rules complicate the 
problem when synthesizing (i.e., our evaluation supports our conjecture.)

\NOTE[DPF]{There is still some clumsiness using our improved DFS, since
at some point, we may want to make this clearer, so have DFS not be fonted
is a little weird.  I think both should always use ourDFS and 
macro expand it to <our improved DFS>.  Then changes will be much easier.}

In general, only \DFSi{} and \DFSbi{} constantly perform well. \DFSf{}
is just as efficient in all benchmarks except those of \veryrecursiveo. Both
implementations of BFS have obvious overhead in many cases. Among the
three variants of DFS, which all have unfair \conj{}, \DFSf{} is most
resistant to clause permutation, followed by \DFSbi{} then
\DFSi{}. Among the two implementation of BFS, our improved \BFS{}
constantly performs as well or better. Interestingly, every strategy
with fair \disj{} suffers in \veryrecursiveo{} and \DFSf{} performs
well elsewhere. Therefore, this benchmark might be a special
case. Fair \conj{} imposes considerable overhead constantly except in
\appendo. The reason might be that strategies with fair \conj{} tend
to keep more intermediate answers in the memory.

@@

Our quantitative evaluation shows that \DFSbi{} and \DFSf{} are competitive 
alternatives to \DFSi{}, the current search strategy miniKanren
and that \BFS{} is less practical.
% and that \BFSser{} is less practical than other breadth-first strategies.

>>>>

\usepackage{listings}
\lstset{
  language=Scheme,
  basicstyle=\ttfamily,
  morekeywords={run,conde,run*,defrel,==,fresh,disj,conj,disj+},
  alsodigit={!\$\%&*+-./:<=>?@^_~},
  morecomment=[l]{;,\#{}lang},
  mathescape=true,
  literate={-inf}{{$^\infty$}}{1} {/fair}{{$_{fair}$}}{3}
  		   {→}{{$\rightarrow$}}{1}
  		   {×}{{$\times$}}{1}
  		   {==}{{$\equiv$}}{1}
  		   {conde}{{\textcolor[rgb]{0,.3,.7}{\textbf{cond$^e$}}}}{4}
           {appendo}{{append$^o$}}{6}
  		   {repeato}{{repeat$^o$}}{6}
  		   {disj2}{{disj$_2$}}{4}
  		   {conj2}{{conj$_2$}}{4}
  		   {g0}{{g$_0$}}{2}
  		   {g1}{{g$_1$}}{2}
  		   {g2}{{g$_2$}}{2}
  		   {g3}{{g$_3$}}{2}
  		   {gl}{{g$_l$}}{2}
  		   {gr}{{g$_r$}}{2}
  		   {DFSi }{{DFS$_{i}$}}{3}
  		   {DFSbi}{{DFS$_{bi}$}}{3}
  		   {DFSf }{{DFS$_{f}$}}{3}
}
%% scheme-list .

@@

\newcommand{\DFSi }[0]{DFS$_{i}$}
\newcommand{\DFSf }[0]{DFS$_{f}$}
\newcommand{\DFSbi}[0]{DFS$_{bi}$}
\newcommand{\BFS}[0]{BFS}
\newcommand{\BFSser}[0]{BFS}
\newcommand{\BFSuni}[0]{our BFS}
\newcommand{\BFSimp}[0]{our improved BFS}

@@

We describe fairness levels in disjunction and conjunction
implementations.  Specifically, a disjunction implementation can be
fair, almost-fair, or unfair. And a conjunction implementation can
be fair or unfair.  We compare the fairness level of four search
strategies: the standard miniKanren interleaving depth-first search,
the balanced interleaving depth-first search, the fair depth-first
search, and the standard breadth-first search.
The two non-standard depth-first searches are new. And we present two new, more 
efficient and shorter implementation of the standard breadth-first search. 
Using 
quantitative evaluation, we argue that the two new depth-first searches are 
competitive alternatives to the standard one, 
and that our breadth-first search implementations are more efficient than 
the current one.

\NOTE[LKC]{``simpler'' -> ``shorter'' (more objective)}

\NOTE[LKC]{We actually have two new BFS implementations, an easy one and an 
improved one (BFSimp/BFSopt). Both of them runs faster than the current BFS. I 
didn't name the easy one because I considered it just a stepstone to BFSimp. 
But now I think giving names to both of them would be more clear.}

@@

\NOTE[DPF]{I have decided to agree with you that we should not use 
BFSser, so I am going to remove all occurrences.  
Also, we should say, ``Our implementation of BFS''
and then say, shortened to ``Our BFS'' and then you can use it in the table,
so one column should be Our BFS and the other should be BFS.}

\NOTE[DPF]{Occurrences of BFS (without Our) mean Seres et al. (We need only say
that once, or very occasionally}

\NOTE[DPF]{Is the spelling of reverso truly written without the last e?
Shouldn't it be reverseo with the appropriate raising of o.}
\NOTE[LKC]{Yes, it is reverso instead of reverseo in Dmitris' paper.}

@@

To summarize our contributions, we
\begin{itemize}
	\item propose and implement \textbf{b}alanced \textbf{i}nterleaving 
depth-first search (\DFSbi{}), a new search strategy with almost-fair \disj{}.
	\item propose and implement \textbf{f}air depth-first search (\DFSf{}), 
a new search strategy with fair \disj{}.
	\item implement in a new way the standard breath-first search (\BFS), a 
search strategy with fair \disj{} and fair \conj{}. We refer to ``the current 
BFS implementation'' (``BFS'' for short) as the implementation by 
\citet{seres1999algebra} and refer to ``our BFS implementation'' (``our BFS'' 
for short) as our new one. We formally prove that the two BFS implementations 
are semantically equivalent, however, our BFS runs faster in all benchmarks and 
is shorter.
\end{itemize}

@@

\NOTE[DPF]{Was this supposed to be a note?
``We never use \texttt{run*} in this paper because fairness is only interesting 
when we have an unbounded number of answers. However, it is perfectly fine to 
use run* with any search strategies.''}
\NOTE[LKC]{I initially wrote it down as a note. I might get it wrong, but I 
thought you suggested me to move it into the paper.}

@@

\begin{figure}
	\lstinputlisting{Figures/BFSuni.rkt}	
	\caption{implementation of \BFSuni{} (based on \DFSf{})}
	\label{BFSuni}
\end{figure}

\BFS{} has both fair \disj{} and fair \conj{}. Our first implementation 
(\autoref{BFSuni}) is based on \DFSf{} (not \DFSi{}). It is so similar to 
\DFSf{} that we only need to apply two changes: (1) rename 
\texttt{append-map$^\infty$} to \texttt{append-map$^\infty_{fair}$} and (2) 
replace \texttt{append$^\infty$} with \texttt{append$^\infty_{fair}$} in 
\texttt{append-map$^\infty$}'s body.

\NOTE[DPF]{I need clarification: Applying the above changes won't result in 
	``our \BFS,'' but yet a third implementation of \BFS?}
\NOTE[LKC]{Improved.}

This implementation is improvable in two ways. First, as mentioned in 
\autoref{sec:fairconj}, \BFS{} puts answers in bags and answers of the same 
cost are in the same bag. In the above implementation, however, 
it is not very clear how we manage cost information --- the \texttt{car}s of a 
search space have cost 0 (i.e., they are all in the same bag), and every thunk 
indicates an increment in cost. It is even more subtle that 
\texttt{append$^\infty_{fair}$} and the \texttt{append-map$^\infty_{fair}$} 
respects the cost information. Second, \texttt{append$^\infty_{fair}$} is 
extravagant in memory usage. It makes $O(n+m)$ new \texttt{cons} cells every 
time, where $n$ and $m$ are the ``length''s of input spaces. \DFSf{} also has 
the space extravagance.

\NOTE[LKC]{I have pointed out ``\DFSf{} also has the space extravagance'' at 
the end of the above paragraph.}

In the following subsections, we first describe \BFSimp{} implementation that 
manages cost information in a more clear and concise way and is less 
extravagant in memory usage. Then we compare \BFSimp{} with \BFSser{}.

\NOTE[DPF]{Let's use one more line and far less horizontal space
by use 3 linefeeds.  They will still align nicely.}
\NOTE[LKC]{fixed}

@@

\begin{figure}
	\lstinputlisting{Figures/BFSimp.rkt}	
	\caption{New and changed functions in our BFS that implements pure 
	features}
	\label{BFSimp}
\end{figure}

@@

@@

\begin{figure}
	\lstinputlisting{Figures/BFSimp-cont.rkt}	
	\caption{New and changed functions in our BFS that implement impure 
		features}
	\label{BFSimp-cont}
\end{figure}

@@

In this subsection, we compare the pure subset of \BFSimp{} with \BFSser{}. We 
focus on the pure subset because \BFSser{} is designed for a pure 
relational programming system. We prove in Coq that these two search strategies 
are are semantically equivalent, since \texttt{(run n ? g)} produces the same 
result in both our BFS and BFS. (See supplements for the formal proof.) To 
compare efficiency, we 
translate \BFS{}'s Haskell code into Racket (See supplements for the 
translated code). The translation is direct due to the similarity of the two 
relational programming systems. The translated code is longer than \BFSimp{}. 
And it runs slower in all benchmarks. Details about differences in efficiency 
are in \autoref{sec:quan}.
% \autoref{compare-efficiency}

@@

\begin{table}
	% run in command line, with a memory limit of 500MB
	\begin{tabular}{|c|c|c|c|c|c|c|c|}
		\hline 
	benchmark & size & \DFSi & \DFSbi & \DFSf & \BFSuni & \BFSimp & \BFSser	\\
		\hline
		\veryrecursiveo & 100000 & 166 & 103 & 412 &   417 &   451 &   1024 \\
	    				& 200000 & 283 & 146 & 765 &   766 &   839 &   1875 \\
						& 300000 & 429 & 346 &2085 &  2066 &  1809 &   4408 \\
		\hline  
		\appendo        & 	 100 &  17 &  18 &  17 &    18 &    17 &     65 \\
		         	  	& 	 200 & 145 & 137 & 137 &   137 &   142 &    121 \\
          		      	&	 300 & 388 & 384 & 387 &   383 &   429 &    371 \\
%   		& - & - & - & - & - & - \\
		\hline 
		\reverso		& 	  10 &   3 &   4 &   3 &    18 &    18 &     36 \\
						& 	  20 &  35 &  35 &  33 &  3119 &  3070 &   3695 \\
						& 	  30 & 329 & 333 & 315 & 76243 & 75079 & 107531 \\
		\hline
		quine-1 		& 1 & 13 & 14 & 10 & - & - & - \\
						& 2 & 30 & 34 & 25 & - & - & - \\
						& 3 & 41 & 48 & 33 & - & - & - \\
		\hline
		quine-2 		& 1 & 22 & 21 & 12 & - & - & - \\
						& 2 & 51 & 46 & 24 & - & - & - \\
						& 3 & 72 & 76 & 32 & - & - & - \\
		\hline
%		quine-1 & 1 &  71 &  44 & 69 & ??? & - & - \\ 
%		& 2 & 127 & 142 & 95 & ??? & - & - \\ 
%		& 3 & 114 & 114 & 93 & ??? & - & - \\ 
%		\hline
%		quine-2 & 1 & 147 & 112 &  56 & ??? & - & - \\ 
%		& 2 & 161 & 123 & 101 & ??? & - & - \\ 
%		& 3 & 289 & 189 & 104 & ??? & - & - \\ 
%		\hline 
		'(I love you)-1 &  99 &  10 &  37 & - &   40 &   40 &   96 \\
						& 198 &  22 &  71 & - &  374 &  374 &  652 \\
						& 297 &  24 & 292 & - & 1707 & 1668 & 3759 \\
		\hline
		'(I love you)-2 &  99 & 485 & 179 & - &   38 &   44 &   94 \\
						& 198 & 808 & 638 & - &  366 &  414 &  630 \\
						& 297 &1265 & 916 & - & 1674 & 1651 & 3691 \\ 
		\hline 
		% The data below is test with old benchmarks
%'(I love you)-1 &  99 & 56 & 15 & 22 & ??? &  74 & 165 \\ 
%& 198 & 53 & 72 & 55 & ??? &  47 &  74 \\
%& 297 & 72 & 90 & 44 & ??? & 181 & 365 \\ 
%\hline
%'(I love you)-2 &  99 & 242 &  61 & 16 & ??? &  66 &  99 \\ 
%& 198 & 445 & 110 & 60 & ??? &  42 &  64 \\
%& 297 & 476 & 146 & 49 & ??? & 186 & 322 \\ 
%\hline 
	\end{tabular}
	\caption{The results of a quantitative evaluation: running times of 
	benchmarks in milliseconds}
	\label{compare-efficiency}
\end{table}

In this section, we compare the efficiency of search strategies. A concise 
description is in Table~\ref{compare-efficiency}. A hyphen means ``running out
of 500 MB memory.'' The first two benchmarks are from 
TRS2. \reverso{} is from 
\citet{rozplokhas2018improving}. 
The next two benchmarks about quine are modified from a similar test case in 
\citet{byrd2017unified}. The modifications are made to circumvent the need for 
symbolic constraints (e.g. $\neq$, \texttt{absent$^o$}).
Our version generates de Bruijnized expressions and prevents closures from 
being inside a list. 
The sibling benchmarks differ in the \conde{} clause order of their relational 
interpreters.
The last two benchmarks are about synthesizing expressions that evaluate to 
\texttt{'(I love you)}. 
They are also modified from a similar test case in \citet{byrd2017unified} 
because of the same reason. 
Our version generates de Bruijnized expressions. 
Again, the sibling benchmarks differ in the \conde{} clause order of their 
relational interpreters. The first one has elimination rules (i.e. application, 
\texttt{car}, and \texttt{cdr}) at the end, while the other has them at the 
beginning. 
We conjecture that \DFSi{} would perform badly in the second case because 
elimination rules complicate the problem when synthesizing (i.e., our 
evaluation supports our conjecture.)

\NOTE[LKC]{I change the benchmark '(I love you) such that it doesn't prevent 
closures from getting into pairs because I consider this restriction not 
reasonable. As for quines, they are already very slow so I didn't make the 
changes.}

\NOTE[DPF]{There is still some clumsiness using our improved DFS, since
at some point, we may want to make this clearer, so have DFS not be fonted
is a little weird.  I think both should always use ourDFS and 
macro expand it to <our improved DFS>.  Then changes will be much easier.}
\NOTE[LKC]{I guess you are talking about ``our improved BFS''. I have added 
relevant macros.}

\NOTE[LKC]{I rewrote the following paragraph and the table to include the 
additional BFS and update the '(I love you) benchmark.

Also, all running time are re-measured by running in command-line. I used to 
run benchmarks with DrRacket. Thus, the time measurements are smaller.}

In general, only \DFSi{} and \DFSbi{} constantly perform well. \DFSf{}
is just as efficient in \appendo, \reverso, and \texttt{quine}s. All BFS
implementations have obvious overhead in most cases. 
Among the three variants of DFS, which all have unfair \conj{}, \DFSf{} is most 
resistant to clause permutation in \texttt{quines}, followed by \DFSbi{} then 
\DFSi{}. \DFSf{}, however, runs out of memory in \texttt{'(I love you)}s. In 
contrast, \DFSbi{} still performs more stable than \DFSi{}. Thus, we consider 
\DFSbi{} a competitive alternative to \DFSi{}, the current standard miniKanren 
search strategy. 
Among the three implementations of \BFS, our \BFS{}s constantly perform as well 
or better. \BFSimp{} only out-performs \BFSuni{} significantly in 
\veryrecursiveo{} 300000, while performing as well or worse elsewhere. The 
reason might be that the size of bags are usually too small to be worried about.
It is hard to conclude how \disj{} fairness affect performance based on these 
statistics. Fair \conj{}, however, imposes considerable overhead constantly 
except in \appendo. The reason might be that those strategies tend to keep more 
intermediate answers in the memory.

@@

Our quantitative evaluation shows that \DFSbi{} and \DFSf{} are competitive 
alternatives to \DFSi{}, the current miniKanren search strategy,
and that \BFS{} is less practical.
% and that \BFSser{} is less practical than other breadth-first strategies.
